---
title: "Travel Itineraries"
---

<style>

/* Page container feel */
body {
  background: #fafafa;
}

/* Section headers */
h2 {
  margin-top: 2rem;
  border-bottom: 2px solid #e5e7eb;
  padding-bottom: 0.3rem;
}

h3 {
  margin-top: 1.5rem;
  color: #374151;
}

/* Card wrapper for each survey table */
.itinerary-card {
  background: white;
  border: 1px solid #e5e7eb;
  border-radius: 14px;
  padding: 1rem 1.25rem;
  margin-bottom: 2rem;
  box-shadow: 0 2px 6px rgba(0,0,0,0.04);
}

/* Clean table styling */
table {
  width: 100% !important;
  font-size: 0.95rem;
  border-collapse: collapse;
}

th {
  background: #f3f4f6 !important;
  position: sticky;
  top: 0;
  z-index: 1;
  font-weight: 600;
}

td, th {
  padding: 0.6rem 0.9rem !important;
  vertical-align: middle !important;
}

/* Center checkmarks */
td:nth-child(3),
td:nth-child(4),
td:nth-child(5),
td:nth-child(6) {
  text-align: center;
  font-weight: 400;
}

/* Link styling */
a {
  color: #2563eb;
  text-decoration: none;
}

a:hover {
  text-decoration: underline;
}

/* “button-like” link for travel info */
a[href*="travel"] {
  display: inline-block;
  padding: 0.25rem 0.6rem;
  background: #eef2ff;
  border-radius: 999px;
  font-size: 0.85rem;
}

/* spacing */
p {
  margin-bottom: 0.5rem;
}

.table-scroll-vert {
  max-height: 450px;   /* adjust as needed */
  overflow-y: auto;
  overflow-x: hidden;
  border: 1px solid #e5e7eb;
  border-radius: 12px;
}

/* keep header visible while scrolling */
.table-scroll-vert thead th {
  position: sticky;
  top: 0;
  z-index: 2;
  background: #f3f4f6 !important;
}

</style>


```{r, results = 'asis', echo = F}
# this code parses the names of the flight itineraries in this year's folder and generates a table with the person's name, what legs they are one, and the confirmation code. Files must be named with the following information in this order: NAME_Leg1_2_CONFIRMATIONCODE

options(knitr.kable.NA = "")
flights_dir <- "../files/travel/flight_itineraries/"
```


```{r, results = 'asis', echo = F}
# ensures code doesn't break if this year's folder hasn't been created yet
year <- as.numeric(format(x = Sys.Date(), format = "%Y"))
year <- ifelse(test = year %in% list.dirs(
  path = flights_dir,
  full.names = F,
  recursive = F
),
yes = as.numeric(x = year),
no = as.numeric(x = year) - 1
)


path0 <- paste0(flights_dir, year)
travel_plans <- stringr::str_remove(string = dir(path0, recursive = TRUE, full.names = TRUE), 
                                    pattern = paste0(path0, "/"))


tmp_table <- tibble(full_file = travel_plans) %>%
  tidyr::separate(full_file, c("survey", "file"), sep = "/", remove = FALSE) %>%
  dplyr::mutate(file = tools::file_path_sans_ext(x = gsub(
    pattern = " ",
    replacement = "_",
    x = file
  ))) %>%
  dplyr::mutate(
    Name = str_extract(file, "^[A-Za-z]+"),
    `Leg 1` = ifelse(grepl("l1|_l.+1", file, ignore.case = T), "✓", ""),
    `Leg 2` = ifelse(grepl("l2|_l.+2", file, ignore.case = T), "✓", ""),
    `Leg 3` = ifelse(grepl("l3|_l.+3", file, ignore.case = T), "✓", ""),
    `Leg 4` = ifelse(grepl("l4|_l.+4", file, ignore.case = T), "✓", ""),
    Conf_No = str_extract(file, "[A-Za-z]+$"),
    Link = paste0(
      "[travel info](", path0, "/",
      gsub(
        pattern = " ",
        replacement = "%20",
        x = full_file
      ),
      ")"
    )
  )

tabl <- tmp_table %>%
  dplyr::select(Name, Survey = survey, `Leg 1`:Link) %>%
  dplyr::mutate(ord = case_when(
    `Leg 1` == "✓" & `Leg 2` != "✓" ~ 1,
    `Leg 1` == "✓" & `Leg 2` == "✓" ~ 2,
    `Leg 2` == "✓" & `Leg 3` != "✓" ~ 3,
    `Leg 2` == "✓" & `Leg 3` == "✓" ~ 4,
    `Leg 3` == "✓" & `Leg 4` != "✓" ~ 5,
    `Leg 3` == "✓" & `Leg 4` == "✓" ~ 6,
    `Leg 4` == "✓" ~ 7
  ),
  Name = str_to_title(
    Name
  )
  ) %>%
  dplyr::arrange(ord, Name) %>%
  dplyr::filter(!duplicated(.[, 1:4])) %>%
  dplyr::select(-ord) %>%
  split(.$Survey)


survey_keys <- names(tabl)

survey_labels <- dplyr::recode(
  survey_keys,
  EBS = "Bering Sea",
  GOA = "Gulf of Alaska",
  AI  = "Aleutian Islands"
)

cat(paste("##", year, "Survey Year"), "\n\n")

for (i in seq_along(survey_keys)) {

  cat(paste0("\n\n### ", toupper(survey_labels[i]), "\n"))

  g <- tabl[[survey_keys[i]]] %>% dplyr::select(-Survey)

 cat("<div class='itinerary-card'>")
cat("<div class='table-scroll-vert'>")

table_html <- kableExtra::kable(
  g,
  format = "html",
  escape = FALSE,
  align = c("l", rep("c", 4), "l")
) %>%
  kableExtra::kable_styling(
    bootstrap_options = c("striped", "hover"),
    full_width = TRUE
  )

cat(as.character(table_html))

cat("</div>")
cat("</div>\n")
}

rm(g, page_dat, tabl, tmp_table, i, page_desc, page_title, 
   path0, surveys, year, travel_plans, flights_dir)
```
