---
title: "Minimum Identification List"
description: "EBS and AI/GOA regions"
---


<style>

/* ===== Page background ===== */
body {
  background: #fafafa;
}

/* ===== Header ===== */
h1 {
  margin-top: 2rem;
  border-bottom: 2px solid #e5e7eb;
  padding-bottom: 0.3rem;
}

/* ===== Card container ===== */
.id-card {
  background: white;
  border: 1px solid #e5e7eb;
  border-radius: 14px;
  padding: 1rem 1.25rem;

  /* wider but responsive */
  width: min(1400px, 98%);
  margin: 2rem auto;

  box-shadow: 0 2px 6px rgba(0,0,0,0.04);

  /* CRITICAL: prevents table spill */
  overflow-x: auto;
}

/* ===== Table styling ===== */
table {
  width: 100% !important;
  border-collapse: separate !important;
  border-spacing: 0;
  font-size: 0.95rem;

  /* allows shrinking instead of overflow */
  table-layout: auto;
}


/* Sticky header */
th {
  position: sticky;
  top: 0;
  background: #f3f4f6 !important;
  z-index: 2;
  font-weight: 600;
  padding: 0.7rem 0.9rem !important;
  border-bottom: 2px solid #e5e7eb !important;
}

/* Cells */
td {
  padding: 0.55rem 0.9rem !important;
  vertical-align: top !important;
  border-bottom: 1px solid #eef2f7;
}

/* Zebra striping */
tbody tr:nth-child(even) {
  background: #fcfcfd;
}

/* First column emphasis (Phylum) */
td:first-child {
  font-weight: 600;
  color: #111827;
}

/* Second column (Taxon) slightly muted hierarchy */
td:nth-child(2) {
  font-weight: 500;
  color: #374151;
}

/* Collapse spacing under table */
.kable-table {
  margin-bottom: 0;
}

/* Small note style (optional future use) */
.small-note {
  font-size: 0.9rem;
  color: #6b7280;
}



</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  error = FALSE,
  results = "asis"
)
```

```{r results='asis'}
x <- min_ID_list %>% 
  dplyr::arrange(Phylum, Taxon)

check_codes <- FALSE

if (check_codes) {

  codes <- readr::read_csv(
    "C:/Users/sarah.friedman/Work/survey_species_outliers/data/oracle/race_data-race_species_codes.csv"
  ) %>%
    janitor::clean_names() %>%
    dplyr::select(species_name, common_name, species_code) %>%
    dplyr::mutate(
      species_name = ifelse(
        grepl("crinoid", common_name, ignore.case = TRUE),
        "Crinoidea",
        species_name
      )
    )

  tabl <- x %>%
    janitor::clean_names() %>%
    dplyr::filter(!is.na(species_code)) %>%
    dplyr::mutate(
      tmp_tax = dplyr::case_when(
        grepl("basket", common_name, ignore.case = TRUE) ~ "Gorgonocephalus eucnemis",
        taxon == "Mysidaecea" ~ "Mysidae",
        TRUE ~ taxon
      )
    ) %>%
    dplyr::left_join(codes, by = c("tmp_tax" = "species_name")) %>%
    dplyr::mutate(
      species_code.y = ifelse(
        is.na(species_code.y),
        species_code.x,
        species_code.y
      )
    ) %>%
    dplyr::filter(
      (taxon == "Crinoidea" & grepl("unid", common_name.y)) |
        taxon != "Crinoidea"
    ) %>%
    dplyr::select(
      phylum:taxon,
      common_name = common_name.x,
      id_guide_available,
      minimum_id_level,
      species_code = species_code.y
    ) %>%
    dplyr::bind_rows(
      x %>% janitor::clean_names() %>% dplyr::filter(is.na(species_code))
    ) %>%
    dplyr::arrange(phylum, taxon)

  colnames(tabl) <- colnames(x)

} else {
  tabl <- x
}

cat("<div class='id-card'>")

k <- kableExtra::kable(
  tabl,
  format = "html",
  escape = FALSE,
  align = rep("l", 6)
) %>%
  kableExtra::kable_styling(
    bootstrap_options = c("striped", "hover"),
    full_width = FALSE
  ) %>%
  kableExtra::collapse_rows(
    columns = 1,
    valign = "top"
  )

cat(as.character(k))

cat("</div>")
```

