---
title: "Alaska Fish ID by Family"
---

<style>

/* Page background */
body {
  background: #fafafa;
}

/* Header */
h1 {
  margin-top: 2rem;
  border-bottom: 2px solid #e5e7eb;
  padding-bottom: 0.3rem;
}

/* Intro text */
p {
  font-size: 1rem;
  color: #374151;
  max-width: 900px;
}

/* Navigation container */
.family-nav {
  display: grid;
  grid-template-columns: repeat(auto-fit, minmax(240px, 240px));
  gap: 0.75rem;
  margin-top: 1.5rem;
  justify-content: center;  
}

/* Link cards */
.family-nav a {
  display: block;
  padding: 0.75rem 0.9rem;
  background: white;
  border: 1px solid #e5e7eb;
  border-radius: 14px;
  text-decoration: none;
  color: #111827;
  font-weight: 500;
  width: 100%;
  text-align: center;
  box-shadow: 0 1px 3px rgba(0,0,0,0.04);
  transition: all 0.15s ease-in-out;
}

.family-nav a:hover {
  transform: translateY(-1px);
  border-color: #c7d2fe;
  background: #f8fafc;
}

.small-note {
  color: #6b7280;
  font-size: 0.9rem;
}

.family-nav {
  margin-top: 2rem;
}

</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  error = FALSE,
  results = "asis"
)
```


```{r links, results='asis', echo=FALSE}
cat("<p>Select a family to view the fish species commonly encountered on our survey.</p>")

cat("<div class='family-nav'>\n")
cat(paste(grps$link, collapse = "\n"))
cat("\n</div>")
```

