---
title: "Species Identification Guides"
---

<style>

/* ===== Page background ===== */
body {
  background: #fafafa;
}

/* ===== Section headers ===== */
h1 {
  margin-top: 2rem;
  padding-bottom: 0.3rem;
  border-bottom: 2px solid #e5e7eb;
}

h2 {
  margin-top: 2rem;
  margin-bottom: 0.75rem;
  color: #111827;
}

/* ===== Taxa card ===== */
.taxa-card {
  background: white;
  border: 1px solid #e5e7eb;
  border-radius: 14px;
  padding: 1rem 1.25rem;
  margin-bottom: 2rem;
  box-shadow: 0 2px 6px rgba(0,0,0,0.04);
}

/* ===== Table styling ===== */
table {
  width: 100% !important;
  font-size: 0.95rem;
  border-collapse: separate !important;
  border-spacing: 0;
}

/* header */
th {
  background: #f3f4f6 !important;
  font-weight: 600;
  padding: 0.7rem 0.9rem !important;
  border-bottom: 2px solid #e5e7eb !important;
}

/* cells */
td {
  padding: 0.6rem 0.9rem !important;
  vertical-align: top !important;
  border-bottom: 1px solid #eef2f7;
}

/* last row cleanup */
tbody tr:last-child td {
  border-bottom: none;
}

/* zebra striping (subtle) */
tbody tr:nth-child(even) {
  background: #fcfcfd;
}

/* ===== Links ===== */
a {
  color: #2563eb;
  text-decoration: none;
}

a:hover {
  text-decoration: underline;
}

/* make reference links feel like “resource chips” */
td a {
  padding: 0.15rem 0.4rem;
  font-size: 1rem;
}

/* ===== Taxa label column emphasis ===== */
td:first-child {
  font-weight: 500;
  color: #111827;
}

/* spacing between groups handled by card */
.kable-table {
  margin-bottom: 0;
}

.resource-chip {
  display: inline-block;
  padding: 0.2rem 0.6rem;
  background: #eef2ff;
  border: 1px solid #dbe3ff;
  border-radius: 999px;
  font-size: 1.5rem;
  <!-- color: #1d4ed8; -->
  text-decoration: none;
  margin-left: 0.5rem;
}

.resource-chip:hover {
  background: #e0e7ff;
  text-decoration: none;
}

.table-scroll-vert {
  max-height: 450px;   /* adjust as needed */
  overflow-y: auto;
  overflow-x: hidden;
  border: 1px solid #e5e7eb;
  border-radius: 12px;
}

/* keep header visible while scrolling */
.table-scroll-vert thead th {
  position: sticky;
  top: 0;
  z-index: 2;
  background: #f3f4f6 !important;
}

</style>

```{r guides, echo = F}
tabl <- taxa_guides %>%
  dplyr::select(title, section, subsection, url_loc) %>%
  dplyr::mutate(
    filename = basename(url_loc),
    taxa = case_when(
      section %in% c("birds", "mammals") ~ "Birds and Mammals",
      section == "fish" ~ "Fishes",
      section == "algae" ~ "Algae",
      TRUE ~ "Inverts"
    ),
    url_loc = stringr::str_replace(url_loc, "\\./files", "\\../files"),
    reference = paste0("[", title, "](", gsub(" ", "%20", url_loc), ")")
  ) %>%
  arrange(taxa, section, subsection, title)
```


```{r, echo = FALSE, results = "asis"}
fish_id <- paste0(
  "<a class='resource-chip' href='./Species_Info_Fish_ID_by_Taxa.html'>ID by Taxa</a>"
)
options(knitr.kable.NA = "")

sec <- unique(tabl$taxa)

for (i in seq_along(sec)) {
  tmp <- tabl %>%
    dplyr::filter(taxa == sec[[i]]) %>%
    mutate(Subsection = ifelse(is.na(subsection), "", str_to_sentence(subsection))) %>%
    dplyr::select(Subsection, Reference = reference) %>%
    dplyr::mutate(has_taxa = !is.na(Subsection)) %>%
    dplyr::arrange(
      has_taxa,
      Subsection,
      Reference
    ) %>%
    dplyr::select(-has_taxa) %>%
    # correct deduplication
    dplyr::group_by(Subsection) %>%
    dplyr::mutate(
      Taxa = ifelse(row_number() == 1, Subsection, "")
    ) %>%
    dplyr::ungroup() %>%
    select(Taxa, Reference) 

  # header
  if (sec[i] == "Fishes") {
    cat(paste0("## ", sec[[i]], "    ", fish_id, "\n\n"))
  } else {
    cat(paste0("## ", sec[[i]], "\n\n"))
  }

  # card wrapper start
  cat("<div class='taxa-card'>\n")
  cat("<div class='table-scroll-vert'>")

  k <- kableExtra::kable(
    tmp,
    format = "html",
    escape = FALSE,
    linesep = "",
    align = c("l", "l"),
    table.attr = "class='kable-table'"
  ) %>%
    kableExtra::column_spec(1, bold = TRUE)

  cat(k)

  # card wrapper end
  cat("</div>")
  cat("\n</div>\n\n")
}
```
