---
title: "`r page_desc`"
description: "`r page_title`"
site: distill::distill_website
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE
)

library(dplyr)
library(purrr)
library(glue)
library(htmltools)
```

<style>
/* --- Section Cap (H2) --- */
h2 {
  margin: 2rem 0 0 0 !important;
  padding: 1rem 1.5rem;
  font-size: 1.7rem !important;
  font-weight: 700;
  color: #111827;
  background: #f3f4f6;
  border: 1px solid #e5e7eb;
  border-radius: 12px 12px 0 0;
}

/* --- The Box Walls --- */
.section-content-body{
  background: #ffffff;
  border-left: 1px solid #e5e7eb;
  border-right: 1px solid #e5e7eb;
  padding: 0.8rem 2rem;
  margin: 0 !important;
}

.section-content-continuation,
.subsection-block {
  background: #ffffff;
  border-left: 1px solid #e5e7eb;
  border-right: 1px solid #e5e7eb;
  padding: 0rem 2rem;
  margin: 0 !important;
}

/* --- The Subsection Headers --- */
h3 {
  margin: 0 !important;
  padding: 0.5rem 2rem 0.5rem 1.5rem;
  font-size: 1.3rem !important;
  font-weight: 600 !important;
  color: #374151;
  background: #ffffff;
  border-left: 1px solid #e5e7eb;
  border-right: 1px solid #e5e7eb;
  border-bottom: none;
  position: relative;
  }

/* --- The Box Bottom (The Fix) --- */
.section-box-footer {
  height: 12px; /* Small buffer */
  background: #ffffff;
  border: 1px solid #e5e7eb;
  border-top: none;
  border-radius: 0 0 12px 12px;
  margin-bottom: 1rem;
}

/* --- Subsection Indent --- */
.subsection-content {
  padding-left: 0.7rem;
  margin: 0 0 1.5rem 0.8rem;
  border-left: 2px solid #f0f0f0;
}

/* --- Resource Items --- */
.resource-item {
  margin: 0;
  padding: 0.15rem 0;
}

.resource-item p {
  margin: 0;
}

.resource-item + .resource-item {
  margin-top: 0.15rem;
  padding-top: 0.15rem;
}

/* title */
.resource-title {
  font-weight: 400;
  font-size: 1.05rem;
  margin-bottom: 0.1rem;
}

.resource-title a {
  text-decoration: none;
  color: #1f2937;
}

.resource-title a:hover {
  color: #111827;
}

/* subtitle */
.resource-subtitle {
  font-style: italic;
  color: #6b7280;
}

/* description */
.resource-description {
  margin-top: 0.1rem;
  font-size: 0.93rem;
  color: #4b5563;
}

/* --- Sidebar TOC --- */
.dt-toc nav ul li ul {
  display: block !important;
}


.d-article h3 {
  margin-bottom: 0 !important;
}

/* Gap Closure */
h2 + .section-content-body,
h3 + .section-content-continuation {
  margin-top: 0 !important;
}


</style>


```{r build_page, results='asis'}

render_entry <- function(df) {
  cards <- pmap_chr(
    df,
    function(...) {
      row <- list(...)
      
      subtitle <- if (!is.na(row$subtitle) && row$subtitle != "") {
        glue('<span class="resource-subtitle">{row$subtitle}</span>')
      } else {
        ""
      }
      
      title_html <- markdown::markdownToHTML(
        text = row$title_link_inline,
        fragment.only = TRUE
      )
      
      desc_html <- markdown::markdownToHTML(
        text = row$descrip,
        fragment.only = TRUE
      )
      
      paste0(
        '<div class="resource-item">',
        '<div class="resource-title">',
        title_html, subtitle,
        '</div>',
        '<div class="resource-description">',
        desc_html,
        '</div>',
        '</div>'
      )
    }
  )
  
  paste(cards, collapse = "\n")
}


render_subsection <- function(df) {
  subsection_name <- unique(df$subsection)
  content <- render_entry(df)
  
  if (!is.na(subsection_name) && subsection_name != "") {
    paste0(
      "\n</div>\n", 
      "\n### ", subsection_name, "\n", 
      "\n<div class='section-content-continuation'>\n", 
      "<div class='subsection-content'>\n",
      content,
      "\n</div>\n"
    )
  } else {
    # REMOVED the 'subsection-block' class here to prevent double borders
    paste0("\n<div class='orphan-content'>\n", content, "\n</div>\n")
  }
}

render_section <- function(df) {
  section_name <- unique(df$section)
  
  subs <- df %>%
    group_split(coalesce(subsection, ""), .keep = TRUE) %>%
    map_chr(render_subsection) %>%
    paste(collapse = "\n")
  
  if (!is.na(section_name) && section_name != "") {
    paste0(
      "\n\n## ", section_name, "\n",
      "\n<div class='section-content-body'>\n", # Start the box
      subs,
      "\n</div>", # Close the content
      "\n<div class='section-box-footer'></div>\n" # This forces the rounded bottom
    )
  } else {
    subs
  }
}

if (nrow(page_dat) > 0) {
  page_dat <- page_dat %>%
  mutate(
    section = trimws(section),
    subsection = trimws(subsection),
    section = na_if(section, ""),
    subsection = na_if(subsection, "")
  ) 
  
  page_dat <- page_dat %>%
    arrange(section, subsection, title)
  
  output <- page_dat %>% 
    group_split(coalesce(section, ""), .keep = TRUE) %>%
    map_chr(render_section) %>%
    paste(collapse = "\n")
  
} else {
  cat("No content available.")
}
```

`r if(exists("output")) output`